---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "man/figures/"
)
```

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/IQSSdevtools)](https://cran.r-project.org/package=IQSSdevtools)
[![Travis-CI Build Status](https://travis-ci.org/IQSS/IQSSdevtools.svg?branch=master)](https://travis-ci.org/IQSS/IQSSdevtools)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/IQSS/IQSSdevtools?branch=master&svg=true)](https://ci.appveyor.com/project/IQSS/IQSSdevtools)

# IQSSdevtools

**This package is in the early stages of development**

The goal of **IQSSdevtools** is to makes it easy to initialize and compile an
R software package that complies with the [IQSS Best Practices for Software
Development and Sustainability (IBPSDS)](https://github.com/IQSS/social_science_software_toolkit/blob/master/iqss_sss_best_practices.md).

The package will contain the following functions:

- `init_iqss_package`: initialize a new IQSS Best Practices for Software
Development and Sustainability compliant package {MINIMALLY WORKING EXAMPLE}

- `check_best_practices`: checks to what extent a package follows the minimal
best practices.

- `add_iqss_package`: identify and add (when possible) missing Best
Practice compliant elements to an existing R package {IN DEVELOPMENT}

    - `add_test_suit`: add just a test suite, including files needed for 
continuous integration.

- `build_iqss_package`: builds and tests IQSS Best Practice elements in an R
package.

- `iqss_lintr`: lints package source code using IQSS R Style Guide
{GUIDE and FUNCTION IN DEVELOPMENT}

- `publish_package`: {GUIDE and FUNCTION IN DEVELOPMENT}


# IQSS Best Practices for R Language Software Development and Sustainability

`init_iqss_package` initializes a skeleton package that allows you to begin to
implement the IQSS Best Practices for Software Development and Sustainability.

**IN DEVELOPMENT**

- **Documentation**: Sets up documentation dynamically generated using [RMarkdown](http://rmarkdown.rstudio.com/)
and [roxygen2](https://CRAN.R-project.org/package=roxygen2). This includes a *README.Rmd*
file along with a package website generated with [pkgdown](https://github.com/hadley/pkgdown).
The README.Rmd file should lay out core information about the package's motivation, methods and
include a dynamically generated "quick-start" example. `init_iqss_package` also creates a
*NEWS.md* file for you to document all changes made to the package by version.

- **License**: Adds a [GPL-3 License](https://www.gnu.org/licenses/gpl-3.0.en.html)

- **Version Control**: Sets up [git](https://git-scm.com/) version control.

- **Public Source Code Hosting**: If a GitHub authentication token is provided
with the `github_auth_token` argument, a new [GitHub](https://github.com/) remote repository is created for the package.

- **Testing**: Sets up the infrastructure for [unit testing](https://en.wikipedia.org/wiki/Unit_testing) with the
[testthat](https://CRAN.R-project.org/package=testthat) package. The basic foundation for external
continuous integration of these unit tests is set up with the
[Travis CI](https://travis-ci.org/) and [Appveyor](https://www.appveyor.com/) services
to run the tests on Linux and Windows operating systems, respectively.

## Install

**IQSSdevtools** is in the early stages of development and is not yet on CRAN.

To install the development version using [devtools](https://CRAN.R-project.org/package=devtools):

```{r eval=FALSE}
library(devtools)

install_github('hadley/pkgdown') # Not currently on CRAN
install_github('r-pkgs/gh') # Not currently on CRAN
install_github("r-pkgs/usethis")
install_github('IQSS/IQSSdevtools')
```

# Example

To initialize a new package called `mypkg` use:

```{r include=FALSE} 
library(IQSSdevtools)
```

```{r eval=FALSE}
library(IQSSdevtools)

init_iqss_package(path = 'mypkg',
                    description = list("Title" = "A Test IQSS Package")
                  )
```

To check the extent to which a package follows the best practices:

```{r}
check_best_practices()
```

# Relationship with `devtools`

**IQSSdevtools** largely builds on the
[devtools](https://CRAN.R-project.org/package=devtools) package. It
wraps many of the **devtools** functions based on the Best Practices. As such,
feel free to use any **devtools** function when developing your package to
add additional elements/run specific functions.
